Structured Versus Decorated Cospans

### 2020-12-01 cospans.tex
removed duplicate paragraph regarding $\Dbl$ in appendix
continue working on 2

\begin{proof}
Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+,0) \to (\Cat,\times, 1)$ be a lax monoidal pseudofunctor as defined in \cref{defn:double_category}.  We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.

@@

$$F(h'h)(x)\cong F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''$$ is the composite one.

@@

(B) edge node [left] {$\stackrel{\alpha}{\cong}$} (D);
together with an isomorphism $F(\alpha)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 
\begin{align*}
\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)$}&\scalebox{.8}{$\to F((m_1+_bm_2)+_cm_3)$} \\
&\scalebox{.8}{$\stackrel{F(\alpha)}{\cong} F(m_1+_b(m_2+_cm_3))$} \\
\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))$}&\scalebox{.8}{$\to F(m_1+_b(m_2+_cm_3))$}
\end{align*}
%%% Kenny: I think we should call this \alpha something else like \kappa, since it's only a component used in building the associator for horizontal composition (which we are calling \alpha), not the entire thing on its own.

@@

\node (A) at (3.75,0) {$\scriptstyle{\cong \tau_a}$};

@@

\node () at (7.625,0) {$\cong$};

@@

(C) edge node [above] {$F(\psi)$} (F)
(C') edge node [above] {$F(\psi)$} (F')

@@

@@

(G) edge node [above] {$\phi_{m_1,m_2} \times 1$} (E)
(G') edge node [above] {$1 \times \phi_{m_2,m_3}$} (E')

@@

@@

 The definition of double category may be found in Definition \ref{defn:double_category}. To show that the pseudofunctor $F$ in the theorem statement induces a double category $F\lCsp$, we must first define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$ and the composition functor $\odot$ which says how to compose two composable horizontal 1-cells or two composable 2-morphisms horizontally: $$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1.$$

The category of objects $F\lCsp_0$ is simply $\A$. The category of arrows $F\lCsp_1$ has $F$-decorated cospans for objects and maps of $F$-decorated cospans as morphisms. Given two vertically composable $F$-decorated cospans:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\node (G) at (1.5,-1) {$\tau \colon F(h)(x) \to x'$};
\node (A'') at (0,-1.5) {$a'$};
\node (A''') at (0,-2.5) {$a''$};
\node (B'') at (1,-1.5) {$m'$};
\node (C'') at (2,-1.5) {$b'$};
\node (C''') at (2,-2.5) {$b''$};
\node (D'') at (1,-2.5) {$m''$};
\node (E'') at (3,-1.5) {$x' \in F(m')$};
\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
\node (G'') at (1.5,-3) {$\tau' \colon F(h')(x') \to x''$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[above] {$i'$} (D)
(C') edge node[above] {$o'$} (D)
(B) edge node [left] {$h$} (D)
(A'') edge node[above]{$i'$} (B'')
(C'') edge node[above]{$o'$} (B'')
(A'') edge node[left]{$f'$} (A''')
(C'') edge node[right]{$g'$} (C''')
(A''') edge node[above] {$i''$} (D'')
(C''') edge node[above] {$o''$} (D'')
(B'') edge node [left] {$h'$} (D'');
\end{tikzpicture}
\]
their composite is given by the composite of the two maps of cospans in $\A$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a''$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b''$};
\node (D) at (1,-0.5) {$m''$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x'' \in F(m'')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f'f$} (A')
(C) edge node[right]{$g'g$} (C')
(A') edge node[above] {$i''$} (D)
(C') edge node[above] {$o''$} (D)
(B) edge node [left] {$h'h$} (D);
\end{tikzpicture}
\]
together with the composite decoration morphism $\tau' F(\tau) \colon F(h'h)(x) \to x'$ in $F(m'')$.
% this was:
% together with the composite morphism of decorations $\tau' \tau \colon F(h'h)(x) \to x'$ in $F(m'')$
%% \tau' \tau was the notation that I was using, but I see why this was misleading. I believe it should be called \tau'(F(h')(\tau)) \instead of \tau' F(\tau), and also with target x''.
 This completes the descriptions of the category of objects $F\lCsp_0 = \A$ and the category of arrows $F\lCsp_1$.

Next, we define the four structure functors $U,S,T$ and $\odot$. The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
\begin{equation}\label{eq:UFCsp}
\begin{tikzpicture}[scale=1.5]
\node (E) at (-1,0) {$a$};
\node (F) at (-.5,0) {$\mapsto$};
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,0) {$\bot_a \in F(a)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\end{equation}
where $\bot_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.  For morphisms, the functor $U$ is defined as:
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$a$};
\node (G') at (-1,-0.5) {$a'$};
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$a$};
\node (C) at (2,0.5) {$a$};
\node (C') at (2,-0.5) {$a'$};
\node (D) at (1,-0.5) {$a'$};
\node (E) at (3,0.5) {$\bot_a \in F(a)$};
\node (F) at (3,-0.5) {$\bot_{a'} \in F(a')$};
\node (H) at (-0.5,0) {$\mapsto$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$f$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$f$} (D)
(G) edge node [left] {$f$} (G');
\end{tikzpicture}
\]
together with the morphism $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$. For the source and target functors $S, T \maps F\lCsp_1 \to F\lCsp_0$, given an object $F\lCsp_1$, which is an $F$-decorated cospan,
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$x \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the source is the object $a$ and the target is the object $b$. Given a morphism of $F\lCsp_1$, which is a map of $F$-decorated cospans,
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[above] {$i'$} (D)
(C') edge node[above] {$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
$$\tau \maps F(h)(x) \to x'$$
the source is the morphism $f$ and the target is the morphism $g$. The three functors $S,T$ and $U$ satisfy the equations $SU=\id_{\A}=TU$.

Next we define the composite functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$, which amounts to defining how we compose two composable $F$-decorated cospans or horizontally compose two maps of $F$-decorated cospans with a common source and target. Given two composable $F$-decorated cospans which we respectively denote by $M$ and $N$, the capitals of their apices:
\node (F) at (4,0) {$n$};
\node (H) at (4,-0.5) {$y \in F(n)$};
(G) edge node[above]{$o'$} (F);
the composite $M \odot N$ is given by taking the pushout of the two cospans in $\A$ over the shared foot which is the object $b$:
(D) edge node [above] {$j_{n}'$} (F)
(A) edge[bend left] node [left] {$\psi j_m i$} (G)
(E) edge[bend right] node [right] {$\psi j_{n}' o'$} (G);
The composite decoration $x \odot y$ on the apex $m+_b n$ is given by:
$$x \odot y = 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$. Given two horizontally composable maps of $F$-decorated cospans which we respectively denote by $\alpha$ and $\beta$:
their horizontal composite $\alpha \odot \beta$ is the pair given by first horizontally composing the two maps of cospans in $\A$:
(A) edge node[above]{$\psi j_m i_1$} (B)
(C) edge node[above]{$\psi j_n o_2$} (B)
(A') edge node [above]{$\psi j_{m'} i_1'$} (D)
(C') edge node [above]{$\psi j_{n'} o_2'$} (D)
together with the decoration morphism $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the following commutative diagram:
\node (C) at (9.25,0.5) {$F(m+_{b} n)$};
\node (C') at (9.25,-0.5) {$F(m' +_{b'} n')$};
(C) edge node [right] {$F(h_1 +_g h_2)$} (C')
(B) edge node [right] {$F(h_1 + h_2)$} (B')
(E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
The middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying square commutes. The decorations $x \odot y$ and $x' \odot y'$ are given respectively by the top and bottom composite of arrows and the decoration morphism $\tau_{\alpha \odot \beta}$ is given by composing $\tau_\alpha \times \tau_\beta$ with the two commuting squares. It is clear that the equations $S(M \odot N)=S(M)$ and $T(M \odot N)=T(N)$ hold, and this finishes defining the four structure functors $U,S,T$ and $\odot$.

Lastly, our double category is required to have an associator $\alpha$ and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities. We will only show the associator $\alpha$, left unitor $\lambda$ and the pentagon identity, as the remaining details will be similar to these.

First we will build the associator $\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$, which will be a globular 2-morphism; in other words, a map of $F$-decorated cospans with identities on the sides. Given three composable horizontal 1-cells $M_1, M_2$ and $M_3$:
\node (I) at (6,0) {$c$};
we first compute $(M_1 \odot M_2) \odot M_3)$ by pushing out the first two cospans followed by the third:
\node (B) at (2,0) {$(m_1 +_b m_2) +_c m_3$};
\node (C) at (4,0) {$d$};
%\node (D) at (3,0) {$x \in F(m)$};
(C) edge node[above]{$$} (B);
as well as the decoration $(x_1 \odot x_2) \odot x_3$ on the apex obtained as explained above. Explicitly, the decoration $(x_1 \odot x_2) \odot x_3) \in F((m_1+_b m_2) +_c m_3)$ is obtained as the composite $$ (x_1 \odot x_2) \odot x_3 \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(\psi)} F((m_1+_{b} m_2)+_{c} m_3)$$where$$\scriptstyle{\zeta_1 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2) \xrightarrow{F(j)} F(m_1+_b m_2) \xrightarrow {\rho^{-1}} F(m_1+_b m_2) \times 1 \xrightarrow{1 \times x_3} F(m_1+_b m_2) \times F(m_3).}$$
The composite $M_1 \odot (M_2 \odot M_3)$ is obtained similarly:
\node (B) at (2,0) {$m_1 +_b (m_2 +_c m_3)$};
\node (C) at (4,0) {$d$};
%\node (D) at (3,0) {$x \in F(m)$};
(C) edge node[above]{$$} (B);
as well as the decoration $x_1 \odot (x_2 \odot x_3)$ on the apex:
$$x_1 \odot (x_2 \odot x_3) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_c m_3) \xrightarrow{\phi_{m_1, m_2 +_c m_3}} F(m_1+(m_2 +_c +m_3)) \xrightarrow{F(\psi)} F(m_1+_{b} (m_2+_{c} m_3))$$with $\zeta_2$ being similar to $\zeta_1$ above. The associator $\alpha$ is then given by the map of $F$-decorated cospans given by the map of cospans
(B) edge node [left] {$\alpha$} (D);
together with the decoration morphism $\tau_\alpha \colon F(\alpha)((x_1 \odot x_2) \odot x_3) \to (x_1 \odot (x_2 \odot x_3))$ that is obtained by pasting various commutative squares together, as we did for a horizontal composite above. The associator $\alpha$ will then satisfy the pentagon identity:
\node (A) at (-0.5,0) {$((M_1 \odot M_2) \odot M_3) \odot M_4$};
\node (B) at (3,1.05) {$(M_1 \odot (M_2 \odot M_3)) \odot M_4$};
\node (C) at (6.5,0) {$M_1 \odot ((M_2 \odot M_3) \odot M_4)$};
\node (D) at (1.5,-1.05) {$(M_1 \odot M_2) \odot (M_3 \odot M_4)$};
\node (E) at (4.5,-1.05) {$M_1 \odot (M_2 \odot (M_3 \odot M_4))$};
(A) edge node [above] {$\alpha \times 1$}(B)
(B) edge node [above] {$\alpha$}(C)
(A) edge node [below] {$\alpha$}(D)
(D) edge node [above] {$\alpha$}(E)
(C) edge node [below] {$1 \times \alpha$}(E);
which we may realize in two stages. First, for the underlying pentagon of maps of cospans in $\A$ commuting due to the fact that $\lCsp(\A)$ is a double category with its own associator that satisfies the pentagon identity, and second, for the pentagon of morphisms of decorations due to the pasting of various commutative squares in $\Cat$.

We next construct the left unitor. Given a horizontal 1-cell $M$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$x \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the left unitor will be a globular 2-morphism $\lambda \colon 1_a \odot M \to M$, where the identity horizontal 1-cell on the object $a$ will once again make use of the trivial decoration on an object introduced earlier.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,0) {$\bot_a \in F(a)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\id_a$} (B)
(C) edge node[above]{$\id_a$} (B);
\end{tikzpicture}
\]
To compose $1_a$ and $M$, we first compose the two cospans in $\A$ by pushing out over their shared object $a$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,1) {$m$};
\node (E) at (4,0) {$b$};
\node (F) at (2,2) {$a+m$};
\node (G) at (2,3) {$a+_{a} m$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\id_a$} (B)
(C) edge node[above]{$\id_a$} (B)
(C) edge node [above] {$i$} (D)
(E) edge node [above] {$o$} (D)
(B) edge node [above] {$j_a$} (F)
(D) edge node [above] {$j_m$} (F)
(F) edge node [left] {$\psi$} (G)
(A) edge[bend left] node [left] {$\psi j_a$} (G)
(E) edge[bend right] node [right] {$\psi j_{m} o$} (G);
\end{tikzpicture}
\]
The composite decoration $\bot_a \odot x$ will be given by the composite
$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\bot_a \times x} F(a) \times F(m) \xrightarrow{\phi_{a,m}} F(a+m) \xrightarrow{F(\psi)} F(a+_{a} m).$$
The left unitor is then the map of $F$-decorated cospans determined by the following map of cospans in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a$};
\node (B) at (1.5,0.5) {$a+_{a} m$};
\node (C) at (3,0.5) {$b$};
\node (C') at (3,-0.5) {$b$};
\node (D) at (1.5,-0.5) {$m$};
\node (E) at (4.5,0.5) {$\bot_a \odot x \in F(a+_{a} m)$};
\node (F) at (4.5,-0.5) {$x \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\psi j_a$} (B)
(C) edge node[above]{$\psi j_m o$} (B)
(A) edge node[left]{$\id_{a}$} (A')
(C) edge node[right]{$\id_{b}$} (C')
(A') edge node [above]{$i$} (D)
(C') edge node [above]{$o$} (D)
(B) edge node [left] {$\ell$} (D);
\end{tikzpicture}
\]
together with the decoration morphism $\tau_\lambda \colon F(\ell)(\bot_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$. The right unitor $\rho$ is similar, the two unitality squares are similar to the associator shown above, and it is clear that the source and target functors applied to the associator and left and right unitors yield identities.

The final property that we will check is the interchange law for 2-morphisms. Suppose that we have four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$ as shown below:
\node (B'') at (1,-1.5) {$m'$};
\node (C'') at (2,-1.5) {$b'$};
\node (C''') at (2,-2.5) {$b''$};
\node (D'') at (1,-2.5) {$m''$};
\node (E'') at (3,-1.5) {$x' \in F(m')$};
\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
\node (G'') at (4,-1.5) {$b'$};
\node (H'') at (5,-1.5) {$n'$};
\node (I'') at (6,-1.5) {$c'$};
\node (G''') at (4,-2.5) {$b''$};
\node (H''') at (5,-2.5) {$n''$};
\node (I''') at (6,-2.5) {$c''$};
\node (J'') at (7,-1.5) {$y' \in F(n')$};
\node (K'') at (7,-2.5) {$y'' \in F(n'')$};
\node (L'') at (1,-3) {$\tau_{\alpha'} \maps F(h_1')(x') \to x''$};
\node (M'') at (5,-3) {$\tau_{\beta'} \maps F(h_2')(y') \to y''$};
(I') edge node [above] {$o_2'$} (H')
(A'') edge node[above]{$i_1'$} (B'')
(C'') edge node[above]{$o_1'$} (B'')
(A''') edge node[above] {$i_1''$} (D'')
(C''') edge node[above] {$o_1''$} (D'')
(B'') edge node [left] {$h_1'$} (D'')
(G'') edge node [above] {$i_2'$} (H'')
(G'') edge node [left] {$g'$} (G''')
(H'') edge node [left] {$h_2'$} (H''')
(G''') edge node [above] {$i_2''$} (H''')
(I'') edge node [above] {$o_2'$} (H'')
(I'') edge node [right] {$k'$} (I''')
(I''') edge node [above] {$o_2''$} (H''');
We may compose these first vertically and then horizontally, or first horizontally and then vertically, and we must show that these two ways of composing yield the same result. Composing first vertically and then horizontally results in:
\node (B) at (2,0.5) {$m+_{b} n$};
\node (C) at (4,0.5) {$c$};
\node (C') at (4,-0.5) {$c''$};
\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''$};
(A) edge node[above]{$ \psi j_m i_1$} (B)
(C) edge node[above]{$ \psi j_n o_2$} (B)
(C) edge node[right]{$k' k$} (C')
(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
whereas first composing horizontally and then vertically results in:
\node (B) at (2,0.5) {$m+_{b} n$};
\node (C) at (4,0.5) {$c$};
\node (C') at (4,-0.5) {$c''$};
\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
(A) edge node[above]{$\psi j_{m} i_1$} (B)
(C) edge node[above]{$\psi j_{n} o_2$} (B)
(C) edge node[right]{$k' k$} (C')
(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
Everything about these two composites appears identical except for the two middle morphisms and the two morphisms of decorations. However, the two maps $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ and $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ are the same universal map realized in two different ways. The two morphisms of decorations $\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)}$ and $\tau_{(\alpha' \alpha) \odot (\beta' \beta)}$ are also the same as they are obtained as two different compositions of four 2-morphisms in $\Cat$, namely first vertically and then horizontally and first horizontally and then vertically. The interchange law for $\Cat$ says that these two composites must be the same as well, and thus the interchange law for our double category $F\lCsp$ is also satisfied.

>>>>

\begin{proof}
Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+,0) \to (\Cat,\times, 1)$ be a lax monoidal pseudofunctor.  We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.

@@

$$F(h'h)(x)\cong F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''$$ is the decoration of the composite.

@@

(B) edge node [left] {$\stackrel{\kappa}{\cong}$} (D);
together with an isomorphism $F(\kappa)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 
%\begin{align*}
%\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times %F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)$}&\scalebox{.8}{$\to F((m_1+_bm_2)+_cm_3)$} \\
%&\scalebox{.8}{$\stackrel{F(\alpha)}{\cong} F(m_1+_b(m_2+_cm_3))$} \\
%\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times %F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))$}&\scalebox{.8}{$\to F(m_1+_b(m_2+_cm_3))$}
%\end{align*}

@@

\node (A) at (3.75,0) {$\scriptstyle{\cong}$};

@@

\node () at (7.625,0) {$\scriptstyle\cong$};

@@

(C) edge node [above] {} (F)
(C') edge node [above] {} (F')

@@

(B) edge node [above] {} (C)
(B') edge node [above] {} (C')

@@

(G) edge node [above] {$\phi_{m_1,m_2} {\times} 1$} (E)
(G') edge node [above] {$1 {\times} \phi_{m_2,m_3}$} (E')

@@

%%% Christina: I erased tau, and also Fpsi because they were not accurate and those arrows are OK to understand - the universal maps from a 'smaller' colimit to a 'bigger' one. If we kept Fpsi's we should write them like F(psi+1) for the first arrow at the top, and that would make the whole thing a bit heavier.

@@
